\vspace{-3.0cm}\large\textbf{A multi-scalar model for system of cities}

### 2019-09-26 Docs/Communications/2019/CCS2019/Abstract/ccs2019.tex
skeleton_slides

\author[1,2,3]{\footnotesize Juste Raimbault}
\affil[1]{\footnotesize UPS CNRS 3611 ISC-PIF, Paris, France, \url{juste.raimbault@polytechnique.edu}}
\affil[2]{\footnotesize CASA, UCL, London, UK}
\affil[3]{\footnotesize UMR CNRS 8504 Géographie-cités, Paris, France}
\date{\vspace{-5ex}}

@@

@@

This contribution introduces a parsimonious multi-scalar model for systems of cities, based on simple dimensions (mainly populations) with stylized processes, but yielding an effective strong coupling between the metropolitan mesoscopic scale and the macroscopic scale of the system of cities. The model couples the spatial interaction model of \cite{raimbault2018indirect} for the macro scale with the reaction-diffusion model for urban form studied by \cite{raimbault2018calibration}. More precisely, urban areas viewed as a population grid are embedded into the macroscopic interaction model. To evolve populations and local urban forms, one time step consists of (i) population differences are computed by the interaction model; (ii) top-down feedback modifies parameters of mesoscopic models, given control parameters to capture typical scenarios (transit-oriented development or sprawl for diffusion, metropolization or uniformization for aggregation); (iii) local urban form are evolved at a given speed conditionally to the population variation; (iv) changes in urban form influence macroscopic interaction range (capturing the impact of local activity on global insertion), by integrating gravity flows in the area with a squared cost function making a compromise between congestion and flows.

The model is applied on synthetic systems of cities typical of a continental range (500km, hierarchy around 1, 20 cities), with initial local population grid configurations as monocentric. Parameter space is explored with the OpenMOLE model exploration software \cite{reuillon2013openmole}, eased by the implementation of the model in scala \cite{model}. First results show a strong impact of the strong meso-macro coupling, such as for example a qualitative inversion of the behavior as a function of interaction range of macroscopic indicators trajectories when switching from a ``transit-oriented development'' scenario

@@

\footnotesize

>>>>

\author[1,2,3]{\footnotesize Juste Raimbault}
\affil[1]{\footnotesize UPS CNRS 3611 ISC-PIF, Paris, France, \url{juste.raimbault@polytechnique.edu}}
\affil[2]{\footnotesize CASA, UCL, London, UK}
\affil[3]{\footnotesize UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France}
\date{\vspace{-5ex}}

@@

% keywords
% Systems of cities
%Multi-scalar model
%Spatial interaction
%Reaction-diffusion

@@

This contribution introduces a parsimonious multi-scalar model for systems of cities, based on simple dimensions (mainly populations) with stylized processes, but yielding an effective strong coupling between the metropolitan mesoscopic scale and the macroscopic scale of the system of cities. The model couples the spatial interaction model of \cite{raimbault2018indirect} for the macro scale with the reaction-diffusion model for urban form studied by \cite{raimbault2018calibration}. More precisely, urban areas viewed as a population grid are embedded into the macroscopic interaction model. To evolve populations and local urban forms, one time step consists of (i) population differences are computed by the interaction model; (ii) top-down feedback modifies parameters of mesoscopic models, given control parameters to capture typical scenarios (transit-oriented development or sprawl for diffusion, metropolization or uniformization for aggregation); (iii) local urban form are evolved with the reaction-diffusion models at a given speed conditionally to the population variations; (iv) changes in urban form influence macroscopic interaction ranges (capturing the impact of local activity on global insertion), by integrating gravity flows in the area with a squared cost function making a compromise between congestion and flows.

The model is applied on synthetic systems of cities typical of a continental range (500km, hierarchy around 1, 20 cities), with initial local population grid configurations as monocentric. Parameter space is explored with the OpenMOLE model exploration software \cite{reuillon2013openmole}, eased by the implementation of the model in scala \cite{model}. First results show a strong impact of the strong meso-macro coupling, such as for example a qualitative inversion of the behavior as a function of interaction range of macroscopic indicators trajectories when switching from a ``transit-oriented development'' scenario (negative feedback of population growth on diffusion) to a ``sprawl'' scenario (positive feedback). Similarly, mesoscopic urban form indicators are significantly influenced by the coupling process.

Further work will consist in more targeted simulation experiments, including specific exploration algorithms such as diversity search for model regimes \cite{reuillon2013openmole}, to test the model as a proof-of-concept of models for policies. Such a model can also be calibrated on real city systems and urban form trajectories, to extrapolate coupling parameters that would be difficult to obtain otherwise. Our contribution is thus a first step towards multi-scalar simulation models for systems of cities.

@@

%\footnotesize
